Jahn-Teller effect with rigid octahedral rotations in perovskites

### 2023-09-22 manuscript/paper.tex
caption, eg fig.

%Similar to the $t_{2g}$ case, 
The average energy slightly shifts at nonzero $\alpha,\beta$
from $3/5\Delta$ by an amount
\begin{align}
E_0^{e_{g}} &= \left(q_A E_0^A +q_B E_0^B\right)D_4/a - (3/5)f_{q_A}\Delta_o,\\
E_0^A &=
\frac{256 \left(5 \left(4 \beta ^2+1\right) \alpha ^2+5 \beta ^2-3\right)}{243 \sqrt{3}}\\
E_0^B &=
(-\frac{1}{12} 5 \left(7 \beta ^2+4\right) \alpha ^2-\frac{5 \beta ^2}{3}+1).
\end{align}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-wts-eg}
\caption{$alpha=10^\circ$ case, $q_A=q_o/2,2q_o$}
\label{fig:e-wts-eg}
\end{center}
\end{figure}

>>>>

%Similar to the $t_{2g}$ case, 
The average energy slightly shifts at nonzero $\alpha,\beta$
from $3/5\Delta$ by an amount
\begin{align}
\label{eq:eg-E0}
E_0^{e_{g}} &= \left(q_A E_0^A +q_B E_0^B\right)D_4/a - (3/5)f_{q_A}\Delta_o,\\
E_0^A &=
\frac{256 \left(5 \left(4 \beta ^2+1\right) \alpha ^2+5 \beta ^2-3\right)}{243 \sqrt{3}}\\
E_0^B &=
(-\frac{1}{12} 5 \left(7 \beta ^2+4\right) \alpha ^2-\frac{5 \beta ^2}{3}+1).
\end{align}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-wts-eg}
\caption{
Energies and character of $e_g$ states.
$E_{\pm}$ and $E_0^{e_g}$
as a function of $\beta$ at $\alpha=10$, 
and same parameters as in Fig.~\ref{fig:t2g-ge-Es}.
At $q_A=q_o/2$ (a,c) where B cage dominates,
$\alpha$ tends to make $\ket{E_{+}}$
more $x^2-y^2$ (see small $\beta$ region),
while $\beta$ tends to do the opposite 
(see large $\beta$ region).
The roles of $\alpha,\beta$ switch
at $q_A=2q_o$ (b,d), where A cage dominates.
We see that the splitting is relatively small as compared to $t_{2g}$ manifold.
Approximate results obtained by a second order expansion of the Hamiltonian given in Eqs.\ref{eq:eg-hiix}-\ref{eq:eg-E0}
are also shown for comparison.
}
\label{fig:e-wts-eg}
\end{center}
\end{figure}
